\documentclass[12pt, a4paper]{article}
%Gummi|065|=)
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage[russian, english]{babel}
\usepackage{enumerate}
\usepackage{comment}
\usepackage{cite}
\usepackage{mathrsfs}
\usepackage{fullpage}
\usepackage{url}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{bm}
\usepackage{braket}

\def\res{\mathop{\operatorname{Res}}\limits}

\begin{document}

\section{Notations}

\subsection{Green's function}

\subsubsection{As the kernel of the resolvent}
Consider the operator $L: X \to X$.

\begin{itemize}
\item Physics notation: $$R(\lambda) = \frac{1}{\lambda I - L}$$
\item Mathematics notation: $$R(\lambda) = \frac{1}{L - \lambda I}$$
\end{itemize} 

TODO: proof that it is an integral operator

$G(x, s; \lambda)$ is the kernel of $R(\lambda)$.


\subsubsection{Green's function of the differential operator}
Differential operator $L$, defined for distributions.

Green's function at point $s$ is a solution (TODO what if there are many?) of 

\begin{itemize}
\item Physics notation: $$L_x G(x, s) = -\delta(x - s)$$
\item Mathematics notation: $$L_x G(x, s) = \delta(x - s)$$
\end{itemize} 

That is, they differ up to sign. We use PHYSICS notation.

Eigenfunction expansion: 

\begin{itemize}
\item Physics notation: $$G(x, s) = -\sum\limits_n \frac{\psi_n(x) \psi_n^*(s)}{\lambda_n}$$
\item Mathematics notation: $$G(x, s) = \sum\limits_n \frac{\psi_n(x) \psi_n^*(s)}{\lambda_n}$$
\end{itemize} 

\section{Short intro into quantum physics}
TODO

\section{Schrodinger's equation}

\subsection{Time-dependent}

$$i \hbar \partial_t \Psi(x, t) = H \Psi(x, t)$$

Particle in an electric (!!!) field:

$$H = - \frac{\hbar^2}{2 m} \nabla^2 + V(x, t)$$


% https://en.wikipedia.org/wiki/Hamiltonian_(quantum_mechanics)#Charged_particle_in_an_electromagnetic_field
TODO what about charge?

\subsection{Time-independent}

If $V(x, t)$ does not depend on time, we can separate the variables:

$\Psi(x, t) = \psi(x) T(t)$.

$$\begin{cases}
i \hbar \partial_t T(t) = E T(t) \\
(- \frac{\hbar^2}{2 m} \nabla^2 + V(x)) \psi(x) = E \psi(x)
\end{cases}$$

Now that we have time-independent states, we can represent any initial state $\psi_0$ (TODO: complete set of eigenstates) in its basis:

$$\psi_0 = \sum\limits_\lambda A_\lambda \psi_\lambda$$

$$\psi(x, t) = \sum\limits_\lambda A_\lambda \psi_\lambda(x) e^{- \frac{i}{\hbar} E_\lambda t}$$

\section{Reflection coefficient and transmission coefficient}
Reflection/transmission coefficients are quantities describing the behaviour of scattered wave (usually at infinity).

Probability current for spin-0 particle.

% TODO https://en.wikipedia.org/wiki/Probability_current#Spin-0_particle_in_an_electromagnetic_field

$$\bm{j}(x, t) = \frac{\hbar}{2 m i} (\psi(x, t)^* \nabla \psi(x, t) - \psi(x, t) \nabla \psi^*(x, t))$$

TODO: write about stationary (scattering) states and omitting time.

$$T = \frac{|j_{trans}|}{|j_{inc}|}$$

$$R = \frac{|j_{refl}|}{|j_{inc}|}$$

These are position dependent and non-scalar values in general. Usually, geometry and symmetries of the scattering problem allows to define the asymptotic region and calculate its integral over scattering cross section, yielding a scalar value.

\section{Free particle in magnetic field}
$$H = \frac{1}{2m} (- i \hbar \nabla - q A)^2$$


Cylindrical coordinates: $(r, \varphi, z)$.

Field $B = (0, 0, B)$, vector potential $A = (0, \frac{1}{2} B r, 0)$. In this gauge, $\nabla \cdot A = 0$.

$$H = \frac{1}{2m}( - \hbar^2 \nabla^2 + i q \hbar (\nabla \cdot A + A \cdot \nabla) + q^2 A \cdot A)$$

$A \cdot \nabla = \frac{1}{2} B \frac{\partial \psi}{\partial \theta}$

$$H = \frac{1}{2m} (- \hbar^2 \nabla^2 + i q \hbar \frac{1}{2} B \frac{\partial \psi}{\partial \theta} + q^2 \frac{1}{4} B^2 r^2)$$

\end{document}
